\documentclass[a4paper]{book}
\usepackage[times,inconsolata,hyper]{Rd}
\usepackage{makeidx}
\usepackage[utf8]{inputenc} % @SET ENCODING@
% \usepackage{graphicx} % @USE GRAPHICX@
\makeindex{}
\begin{document}
\chapter*{}
\begin{center}
{\textbf{\huge Package `mergekobodata'}}
\par\bigskip{\large \today}
\end{center}
\begin{description}
\raggedright{}
\inputencoding{utf8}
\item[Type]\AsIs{Package}
\item[Title]\AsIs{What the Package Does (Title Case)}
\item[Version]\AsIs{0.1.0.9000}
\item[Author]\AsIs{Who wrote it}
\item[Maintainer]\AsIs{The package maintainer }\email{yourself@somewhere.net}\AsIs{}
\item[Description]\AsIs{More about what it does (maybe more than one line)
Use four spaces when indenting paragraphs within the Description.}
\item[License]\AsIs{GPL-3}
\item[Encoding]\AsIs{UTF-8}
\item[LazyData]\AsIs{true}
\item[Suggests]\AsIs{testthat,
rmarkdown}
\item[Imports]\AsIs{knitr,
plyr}
\item[RoxygenNote]\AsIs{6.1.1}
\item[VignetteBuilder]\AsIs{knitr}
\end{description}
\Rdcontents{\R{} topics documented:}
\inputencoding{utf8}
\HeaderA{merge\_kobo\_data}{Merging data files from deviating kobo tools}{merge.Rul.kobo.Rul.data}
%
\begin{Description}\relax
Merging data files from deviating kobo tools
\end{Description}
%
\begin{Usage}
\begin{verbatim}
merge_kobo_data(folder, filename_pattern = ".", output_file = NULL,
  write_log = T, use_regex = F, add_file_reference = T, verbose = T)
\end{verbatim}
\end{Usage}
%
\begin{Arguments}
\begin{ldescription}
\item[\code{folder}] the path to the folder containing the files to be merged. The files must be in csv format.

\item[\code{filename\_pattern}] a search term to find files that should be merged (inside the folder). You can use R style 'regex' patterns if you set use\_regex=T

\item[\code{output\_file}] full path to the file the merged dataset should be written to. If NULL (default), no output file is written.

\item[\code{write\_log}] if TRUE, writes an html file with a log of the merge and subsequent checks.

\item[\code{use\_regex}] if TRUE, searches the 'folder' directory for 'filename\_pattern' using regex patterns. Defaults to FALSE.

\item[\code{add\_file\_reference}] If TRUE (default), adds a new column called `MERGED\_FROM\_FILE` containing the file name of each records source file.

\item[\code{verbose}] if TRUE writes messages to console during merge; set to FALSE to make quiet.
\end{ldescription}
\end{Arguments}
%
\begin{Value}
the merged data frame.
\end{Value}
\printindex{}
\end{document}
